Untitled

### 2018-10-22 Rmd/prueba_plot_family.Rmd
Step by step...

a <- ggplot(pein_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="A) Petunia",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

#Colur per family
#Different colour per family
b <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="B) Capsicum",x="", y = "")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
#Different colour per family
c <- ggplot(soly_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="C) Tomato",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

#Different colour per family
d <- ggplot(some_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="D) Eggplant",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

>>>>

a <- ggplot(pein_seed_set_final, aes(x = factor(Family, levels=unique(Family)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="A) Petunia",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

#Colur per family
#Different colour per family
b <- ggplot(caan_seed_set_final, aes(x = factor(Family, levels=unique(Family)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="B) Capsicum",x="", y = "")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
#Different colour per family
c <- ggplot(soly_seed_set_final, aes(x = factor(Family, levels=unique(Family)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="C) Tomato",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

#Different colour per family
d <- ggplot(some_seed_set_final, aes(x = factor(Family, levels=unique(Family)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="D) Eggplant",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=7,out.width='100%'}
library(dplyr)

#load libraries
library(reshape2)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(grid)
library(lattice)
library(gtable)

cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")

##
###
#B. OLERACEA
###
##
#

brol_seed_set_final <- read.csv("Data/brol_seed_set_final.csv")
brol_seed_set_final=brol_seed_set_final[,-1]
#Different colour per family
a <- ggplot(brol_seed_set_final, aes(x = factor(Family, levels=unique(Family)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="A) Wild cabagge",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

#
##
###
#B. RAPA
###
##
#

brra_seed_set_final <- read.csv("Data/brra_seed_set_final.csv")
brra_seed_set_final=brra_seed_set_final[,-1]

#Different colour per family
b <- ggplot(brra_seed_set_final, aes(x = factor(Family, levels=unique(Family)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="B) Pak choi",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

#
##
###
#E. VERSICARIA
###
##
#

ersa_seed_set_final <- read.csv("Data/ersa_seed_set_final_common_names.csv")
ersa_seed_set_final=ersa_seed_set_final[,-1]

#Different colour per family
c <- ggplot(ersa_seed_set_final, aes(x = factor(Family, levels=unique(Family)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="C) Rocket",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

##
###
#S. ALBA  
###
##
#

sial_seed_set_final <- read.csv("Data/sial_seed_set_final_common_names.csv")
sial_seed_set_final=sial_seed_set_final[,-1]

#Different colour per family
d <- ggplot(sial_seed_set_final, aes(x = factor(Family, levels=unique(Family)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="D) White mustard",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

grobz <- lapply(list(a, b, c, d), ggplotGrob)
grobz.plot <- arrangeGrob( grobs = list(rbind(grobz[[1]], grobz[[3]], size = "last"),
                                        rbind(grobz[[2]], grobz[[4]], size = "last")), ncol = 2,top="Brassicaceae Focal species")

```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3.7, fig.width=7,out.width='100%'}

library(reshape2)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(grid)
library(lattice)

#Preparing seed set plots, starting with Petunia
#
##
###
#I. AQUATICA
###
##
#
ipaq_seed_set_final <- read.csv("Data/ipaq_seed_set_final_common_names.csv")
ipaq_seed_set_final=ipaq_seed_set_final[,-1]

cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")

#Different colour per family
a <- ggplot(ipaq_seed_set_final, aes(x = factor(Family, levels=unique(Family)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="A) Water morning glory",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

#IPPU
ippu_seed_set_final <- read.csv("Data/ippu_seed_set_final_common_names.csv")
ippu_seed_set_final=ippu_seed_set_final[,-1]

#Different colour per family
b <- ggplot(ippu_seed_set_final, aes(x = factor(Family, levels=unique(Family)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="B) Morning glory",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

#There are 3 crosses were seeds were lost (2,7,9)
#load libraries

#read data and cleaning

gl <- lapply(list(a,b), ggplotGrob)
library(grid)
widths <- do.call(unit.pmax, lapply(gl, "[[", "widths"))
heights <- do.call(unit.pmax, lapply(gl, "[[", "heights"))
lg <- lapply(gl, function(g) {g$widths <- widths; g$heights <- heights; g})

grobz <- lapply(list(a, b), ggplotGrob)
grobz.plot <- arrangeGrob(grobs = list(rbind(grobz[[1]], size = "last"),
                                        rbind(grobz[[2]], size = "last")), ncol = 2,top="Convolvulaceae")

load("legend.rda")
grid.newpage()
grid.draw(legend)

```
